### 2022-06-07 paper/ase22/CM/coverage.tex
final paper

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/covergae.pdf}
    \caption{The coverage results of the generated test
      samples. \sw{Make the figures larger.}}
    \label{fig:coverage}
\end{figure}

Fig. \ref{fig:coverage} shows the coverage results of the generated
test samples, where the red line represents \tool and the black line
represents \Cklst.  Each column in Fig. \ref{fig:coverage} represent
the results for one NLP model, the first row is the \textit{BoundCov}
results and the second row is the \textit{SActCov} results.  From the
results, we make two observations observations. First, for \emph{all}
experimental settings (\eg NLP model, coverage metric), \tool achieves
high coverage than \Cklst. Recall that a higher coverage implies the
test case in the test suite is more diverse and rarely to have a
statistical distribution similar to the model training data. As a
result, a test suite with greater coverage complements the model
training data distribution (\ie hold-out testing data) better.  The
experimental results confirm that \tool can generate more diverse test
cases to complement the hold-out testing data for testing NLP models.
\sw{What does the growth trend in each figure indicate?} \sw{Does the
  absolute numbers or relative difference of the two lines on y axis
  mean anything concrete? E.g., how significant is the improvement in
  diversity?}

Another interesting finding is that for each NLP model, there is no
fixed relationship between \textit{BoundCov} and \textit{SActCov}. In
other words, while a test suite may produce higher \textit{BoundCov}
for some models, the same test suite may get higher \textit{SActCov}
for other NLP models.  Recall that \textit{BoundCov} measures both the
upper and lower corner neurons and \textit{SActCov} measures only the
upper corner neurons.  Such observation implies that the upper and
lower corner neurons are distributed unevenly, and measuring only one
of them is not enough.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/coverage.pdf}
    \vspace{-4mm}
    \caption{Coverage results of \tool and \Cklst test cases.}
    \label{fig:coverage}
\end{figure}

Next, Figure \ref{fig:coverage} shows the coverage results of \tool and \Cklst test cases. The red line represents \tool coverage and the black line represents \Cklst coverage. Each column in Figure \ref{fig:coverage} represents the results for one NLP model. The first row is the \textit{BoundCov} results and the second row is the \textit{SActCov} results.

We made three observations.
First, for \emph{all} experimental settings (i.e., NLP model and coverage metric), \tool achieves higher coverage than \Cklst. Recall that a higher coverage implies the test cases are more diverse and do not have a similar statistical distribution to the model training data. As a result, a test suite with greater coverage complements the model training data distribution (\ie holdout testing data) better.
For example, for the first NLP model under test, \tool can achieve a higher coverage than \Cklst with only half the number of test cases.
This result confirms that \tool can generate more diverse test cases to complement the holdout dataset for testing NLP models.

Second, as the number of test cases increases, the test suite can achieve better coverage. Such observation is intuitive. However, generating a more extensive test suite is not easy, particularly  for \Cklst, which is a manually template-based approach.

Third, for each NLP model, there is no fixed relationship between \textit{BoundCov} and \textit{SActCov}. In other words, while a test suite may produce higher \textit{BoundCov} for some models, the same test suite may get higher \textit{SActCov} for other NLP models.
Recall that \textit{BoundCov} measures both the upper and lower corner neurons and \textit{SActCov} measures only the upper corner neurons. 
Such observation implies that the upper and lower corner neurons are distributed unevenly, and measuring only one of them is not enough.

### 2022-06-07 paper/ase22/abstract.tex
final paper

\begin{abstract}
  \Nlp (NLP) technique has become one of the core techniques for
  developing text analytic applications.  These applications are
  required to achieve high reliability to be useful in practice.  The
  trustworthiness of the prevalent NLP applications is obtained by
  measuring the accuracy of the applications on held-out dataset.
  However, evaluating NLP on testset with the held-out accuracy is
  limited in validating its overall quality because the held-out
  datasets are often not comprehensive. Along with this, evaluating an
  NLP model on task-specific behaviors defined on empirical linguistic
  capabilities has been introduced. However, such evaluation relies on
  manually created test cases, and is still limited to measure the
  model performance on biased dataset. In this work, we introduce
  \tool, an NLP model testing infrastructure.  Given a linguistic
  capability that users want to evaluate for a NLP model, \tool finds
  suitable seed inputs from existing datasets, generates sufficient
  number of new test inputs by fuzzing the seed inputs based on their
  \cfg (CFG).  We evaluate \tool by showing its reliability on
  generated inputs and its generalization ability.  In our
  experiments, we also show that \tool facilitates identification of
  critical failures and its origins in the NLP models for \sa task.
\end{abstract}

>>>>

\begin{abstract}
  \Nlp (NLP) technique has become one of the core techniques for
  developing text  analytic applications.  These applications need to achieve high
  reliability to be useful in practice.  The trustworthiness of the NLP applications is often obtained by measuring the accuracy of
  the applications on holdout datasets. However, evaluating NLP on the accuracy of the holdout datasets is limited in validating its overall
  quality because these datasets are often not
  comprehensive. To address this limitation, evaluating an NLP model on
  task-specific behaviors defined on linguistic
  capabilities has been introduced. However, such evaluation relies on manually
  created test cases, and  is still limited to measure the model
  performance on limited datasets. In this work, we introduce \tool,
  an NLP model testing infrastructure.  Given a linguistic capability that users want to evaluate for a NLP model, \tool finds suitable seed inputs
  from existing datasets, generates sufficient number
  of new test inputs by expanding the seed inputs based on their \cfg
  (CFG).  We evaluate \tool by showing that it can generate test cases that are more diverse than an existing approach.
  We also show that \tool facilitates
  identification of critical failures and its origins in the NLP models
  for the \sa task.
\end{abstract}

% \begin{abstract}
%   \Nlp (NLP) technique\jl{technique, model, application?} becomes one of the core techniques for developing
%   text analytics applications.  For developing the NLP applications,
%   the applications are required to achieve high reliability before they
%   go to market\jl{<-simplify the sentence}.  The trustworthiness of the prevalent NLP
%   applications is obtained by measuring the accuracy of the
%   applications on test dataset.  However, evaluating NLP on
%   testset \jl{does with held-out accuracy??} is limited to show its quality
%   because the test datasets are often not comprehensive \jl{what does it mean?}. While the behavioral testing over multiple general linguistic capabilities are
%   employed, it relies on manually created test cases, and is still
%   limited to measure its comprehensive performance for each linguistic
%   capability \jl{does not make sense in terms of story telling}. In this work, we introduce \tool, an NLP model
%   testing methodology. Given a linguistic capability, The
%   \tool finds relevant testcases to test the linguistic
%   capability from existing datasets as seed inputs, generates
%   sufficient number of new test cases by fuzzing the seed inputs based
%   on their \cfg (CFG) \jl{<-long sentence}. We illustrate the usefulness of the \tool by showing input diversity and identifying
%   critical failures in \sota models for NLP task. In our experiment,
%   we show that the \tool generates {} more test cases with {}
%   higher diversity, and finds {} more bugs. \jl{describe what lc is about in a sentence} \jl{need to mention the result with numeric values}

% \end{abstract}

### 2022-06-07 paper/ase22/concl.tex
final paper

\section{Conclusions}
\label{sec:concl}

In this paper, we present \tool automatically that finds and generates
suitable seed test cases for each \lc. \tool fuzz the seeds into a
sufficient number of test cases by expanding \cfg of the seed inputs.
We evaluated \sa models on the generated test cases and anlyzed its
impact on testing the models. Further, we examined failure-inducing
cases for seeking the root of the bug.  We also studied the quality of
\tool test cases by measuring their consistencies with their test
oracles and \lc. These led to show generalization ability of \tool for
model evaluation and its reliability in the end. Our work stands to
provide automated and comprehensive NLP model testing tool.

>>>>

\vspace{-6pt}
\section{Conclusions}
\label{sec:concl}

In this paper, we present \tool that automatically searches and generates seed test cases for each \lc. \tool expands the seeds into a
sufficient number of test cases based on \cfg, covering diverse syntactic structures.
We evaluated \sa models on the generated test cases. It is shown that \tool ensures quality of test cases by showing consistency of test oracle with its input sentence and its \lc. In addition, we showed that diversity in \tool test cases leads to cover more region in \sa models, resulting in higher reliability on the testing. We also examined failure-inducing
cases to understand the root causes of the bugs. These results demonstrate the correctness and usefulness \tool for
model evaluation.

### 2022-06-07 paper/ase22/experiment.tex
final paper

\sw{We may miss a RQ for the test results using \tool. In the setup,
  we have not said which sentiment analysis models we tested, and how
  we measure the results (e.g., number of misclassified test cases).}

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate consistent test sentence and
  its oracle?
\item \label{rq:two}: Are \tool generated test cases relevant to be used
  for their \lc evaluation?
\item \label{rq:three}: Can \tool generate more diverse test cases
  than \Cklst?
\item \label{rq:four}: Can \tool be useful to find root causes of bugs
  in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

\sw{Make clear (earlier in the paper): a test case is a sentence in a
  linguistic capability with a sentiment label.}

@@

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three leaerning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
searching seeds and expanding the seeds in \tool.
%% \TODO{introduce details about each model}

\paragraph{\textbf{Comparison Baselines.}}
We compare our approach with
\Cklst\footnote{https://github.com/marcotcr/checklist}, which is a
manual template-based approach to generate test cases. In this
experiment, we used the \Cklst released \sa test cases which are
generated from its publicly available jupyter notebook implementation.
%% \TODO{introduce details about CHECKLIST}

@@

\paragraph{\textbf{RQ1 and RQ2}} As described in Section \ref{sec:approach},
\tool generates test cases in two steps: specification-based seed
generation and syntax-based sentence expansion. These automated steps
may generate seed/expanded sentences marked with incorrect sentiment
labels or categorized into wrong linguistic capabilities. For example,
the search rule and template defined in a linguistic capability may
not always generate seed sentences in that capability or with the
correct label.  To answer RQ1 and RQ2, we perform a manual study to
measure the correctness of the sentiment labels and linguistic
capabilities associated with the seed/expanded sentences, produced by
\tool.

In the manual study, we randomly sample three sets of pairs of seed
sentences and corresponding \lc from seed test cases. For each set, we
also select expanded sentences that \tool generated from the formerly
sampled seed sentences. In this experiment, each set has 100 sentences
(50 from seed sentences and 50 from expanded sentences) and 200
sentences, in total, are used for the manual study. For each sampled
set, two subjects are provided with the same set of sampled
sentences. The subjects are asked for scoring the two following:
\textbf{1. relevancy score between sentence and its associated \lc}:
this score measures the amount of appropriateness of the use of
sentence for evaluating the model on its \lc.  The scores are discrete
ranging from 1 to 5, and each represents ``strongly not relevant'' to
``strongly relevant'' respectively. \textbf{2. sentiment score of
  sentence}: this score measures the level of sentence sentiment. It
is also discrete, and it ranges from 1 to 5 representing ``strongly
negative'' to ``strongly positive'' respectively. In this work, we
collect manual study scores from 3 subjects in total. In case of
different scores with a same sentence from different subjects, we used
their average score as a score of the sentence.
%% \sw{6 or 3 participants? What happened if participants scored differently?}
From the collected scores, we measure the following metrics:

\begin{eqnarray}
  sentiment\_relecancy &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:srel} \\
  LC\_relevancy_{AVG} &= \frac{1}{\#data}\cdot\sum_{i} LC\_relevancy_i \label{metric:lcrel}
\end{eqnarray}

The equation~\ref{metric:srel} represent the number of test cases that
their labels assigned from are different between \tool and
human. Higher number of this metric indicates worse correlation of
test oracle that \tool generated with human. In addition, the
equation~\ref{metric:lcrel} represents the average score of the
relevancy score between sentence and its associated \lc. Higer average
score means that higher human-level agreement of the use of sentence
for its \lc, resulting in higher suitability of the use of the
testcases for evaluating model on the \lc. Given the metrics, we
answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
and equation~\ref{metric:lcrel} respectively, thereby, show its
ability of \tool to understand human intelligence.

\paragraph{RQ3.}
Recall that a key limitation of \Cklst is that its template-based
approach that relies on significant manual efforts may not generate
test cases that comprehensively cover the sentences in a linguistic
capability. \tool, instead, automatically generates test cases based
on a search dataset and the syntax in a large reference corpus. We
expect \tool can generate a more diverse test suite than \Cklst. To
measure diversity, we follow the approach presented by Ma et
al. \cite{ma2018deepgauge}, where the authors measure the coverage of
NLP model intermediate states as corner-case neurons.  Because the
matrix computation of intermediate states impacts NLP model
decision-making, a test suite that covers a greater number of
intermediate states can represent more NLP model decision-making,
making it more diverse.  Specifically, we used two coverage metrics in
existing work \cite{ma2018deepgauge}, \textit{boundary coverage}
(BoundCov) and \textit{strong activation coverage} (SActCov), as our
metrics to evaluate the test suite diversity.  \TODO{It is worth
  noting that a test sample with a statistical distribution similar to
  the training data would rarely be found in the corner case
  region. As a result, covering a larger corner case region means that
  the test suite is more likely to be buggy.}

@@

\noindent Eq. \ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n, low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.

@@

\noindent The formal definition of our coverage metrics are shown in Eq.\ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.

@@

To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds. After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.

@@

\paragraph{RQ4.}

To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input). Still, it is unclear why mutating one token will cause the model to produce misclassified results.
We seek to help developers to understand why such mutation will result in the misclassification. 
Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences). Motivated by such intuition, we seek to identify a minimal set of input tokens that dominate the model prediction.

Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token in $x$ or not.
The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as

\begin{equation}
    P(f(T(x)) = f(x)) \ge P_{thresh}
    \label{eq:prob}
\end{equation}

To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{}. Following that, we begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Eq. \ref{eq:prob}.
We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Eq. \ref{eq:prob}
Because we iterate the size of our mask, the generated template $T$ will keep the minimum number of tokens in $x$. Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).

@@

\noindent\textbf{Implementation Details.}

\sw{Missing: environment running these experiments.}

>>>>

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:three}: Can \tool generate more diverse test cases
  than \Cklst?
\item \label{rq:one}: Can \tool generate test sentences with correct sentiment labels?
\item \label{rq:two}: Are \tool generated test sentences correctly categorized into a \lc?
\item \label{rq:four}: Can \tool be useful to find root causes of bugs
  in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

@@

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three learning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on the \sa task. In this experiment, we use \Sstt \cite{socher2013sst} dataset for
searching the seeds in \tool. \Sstt is a
corpus of movie review, and consists of 11,855 sentences
with sentiment scores. We split the
scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign 
negative, neutral and positive labels, respectively. In addition, 
we use \Swn as the word sentiment dataset~\cite{baccianella2010sentiwordnet}. 
\Swn is a publicly available English sentiment lexicons.  
It provides lexical sentiment scores and the sentiment word labels 
are categorized by implementing the rules in~\cite{mihaela2017sentiwordnetlabel}.
%% \TODO{introduce details about each model}

\paragraph{\textbf{Comparison Baseline.}}
We compare \tool with
\Cklst,\footnote{https://github.com/marcotcr/checklist} a
manual template-based approach to generate test cases. In this
experiment, we used the \Cklst released \sa test cases which are
generated from its publicly available jupyter notebook implementation.
%% \TODO{introduce details about CHECKLIST}

@@

\paragraph{\textbf{RQ1.}}
Recall that a key limitation of \Cklst is that its template-based
approach relies on significant manual efforts and may not generate test cases that comprehensively cover the sentences
in a linguistic capability. \tool, instead, automatically generates test cases based on a search
dataset and the syntax in a large reference corpus. 
We expect \tool can generate a more diverse test suite than \Cklst, and achieve
more probable evaluation results.

We first evaluate the three \sa
models by testing them on the \tool generated test cases, reporting number of test cases and each model's failure rate in each linguistic capability.

Next,
to measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
Because the matrix computation of intermediate states impacts NLP model decision-making, a test suite that covers a greater number of intermediate states can represent more NLP model decision-making, making it more diverse.
Specifically, we used two coverage metrics by Ma et al. \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), to evaluate the test suite diversity.
It is worth noting that a test sample with a statistical distribution similar to the training data would rarely be found in the corner case region. As a result, covering a larger corner case region means that the test suite is more likely to be buggy.

@@

\noindent Equation \ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.

@@

\noindent The formal definition of our coverage metrics are shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.

@@

To answer RQ1, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds. After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.

@@

\paragraph{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
\tool generates test cases in two steps: specification-based seed
generation and syntax-based sentence expansion. These automated steps
may generate seed/expanded sentences marked with incorrect sentiment
labels or categorized into wrong linguistic capabilities. For example,
the search rule and template defined in a linguistic capability may
not always generate seed sentences in that capability or with the
correct label.  To answer RQ2 and RQ3, we performed a manual study to
measure the correctness of the sentiment labels and linguistic
capabilities associated with the seed/expanded sentences, produced by
\tool.

In the manual study, we randomly sample 100 seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set). For each sampled seed sentence, we randomly obtain one of its expanded sentences.
This forms the two sets of sentences (200 sentences in total) we use for this study, each with 50 seeds and 50 corresponding expanded sentences.
We recruited three participants of this study; all of them are graduate students with no knowledge about this work. 
2 of them were assigned one set of sentences and the third was assigned the other set.
Each participant was asked to provide two scores for each sentence.
\emph{(1) Relevancy score between sentence and its associated \lc}:
this score measures the correctness of \tool linguistic capability categorization.  The scores are discrete,
ranging from 1 (``strongly not relevant'') to 5 (``strongly relevant''). \emph{(2) sentiment score of the sentence}: this score measures the sentiment level of the sentence . It
is also discrete, ranging from 1 (``strongly
negative'') to 5 (``strongly positive''). 
We measure the following:

\begin{eqnarray}
  sent\_consistency &= \frac{1}{\#Sample\cdot~}\cdot \sum_{i} \delta(label_{S^2LCT}=label_{human}) \label{metric:srel} \\
  LC\_relevancy_{AVG} &= \frac{1}{\#Sample\cdot~}\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
\end{eqnarray}

Equation~\ref{metric:srel} represents the percentage of the test cases that \tool and the participants produce the same sentiment labels. High value of this metric indicates \tool generates test cases with correct labels. Equation~\ref{metric:lcrel} represents the average of the
normalized relevancy score between a sentence and its associated
\lc. Higher average score means indicates the linguistic capability categorization by \tool is correct. We answer RQ2 and RQ3 using the metrics defined by
Equation~\ref{metric:srel} and Equation~\ref{metric:lcrel},
respectively.

\paragraph{\textbf{RQ4.}}

To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input). Still, it is unclear why mutating one token will cause the model to produce misclassified results.
We seek to help developers understand why such mutation will result in the misclassification. 
Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences). Motivated by such intuition, we identify a minimal set of input tokens that dominate the model prediction.

Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token (\ie $tk_i$) in $x$ or not.
The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
\begin{equation}
    P(f(T(x)) = f(x)) \ge P_{thresh}
    \label{eq:prob}
\end{equation}
To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{lemna}. We then begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Equation \ref{eq:prob}.
We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Equation \ref{eq:prob}.
Because we iterate the size of the mask, the generated template $T$ will keep the minimum number of tokens in $x$. Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).

@@

% \noindent\textbf{Implementation Details.}

% \sw{Missing: environment running these experiments.}

### 2022-06-07 paper/ase22/result.tex
final paper

This section presents experiment results and answer the RQs by
studying the results quantatively and qualitatively.

\InputWithSpace{tables/manual-study-table}
\InputWithSpace{tables/test-results-table}

\subsection{RQ1: \tool Sentiment Label Consistency}
Table~\ref{table:ManualStudy} shows the statistics of scores collected
from the manual study of \tool. First column represents type of test
case. The number of test cases used for the study is represented in
second column. Label consistency score and \lc relevancy score defined
at equation~\ref{metric:srel} and~\ref{metric:lcrel} are shown at the
remaining columns. First, it is shown that high label consistency
score over 0.8. It means that \tool generates test oracles consistent
to human understanding. It is also observed that there is no
difference of the scores between seed and expanded sentences. The
observation implies that the expansion method in \tool preserves
sentiment of expanded sentences as its seed, and provides its
reliability. These observations answer RQ1 and conclude that \tool
generates test case with high consistency between test sentence and
its oracle.

\subsection{RQ2: Correctness of Linguistic Capability Categorization}
The result in table~\ref{table:ManualStudy} also shows that \tool
achieves high order of agreement with human assessment on \lc
relevancy. In parallel, it is observed that the expanded sentences
generated from \tool also have same level of \lc
relevancy. Accordingly, we answer the RQ2 by concluding that
\tool generates \lc relevant test cases with the agreement with human.

\jl{The following needs to be in RQ2 result section after simin
  completes RQ2 result section} Table~\ref{table:TestResult} shows
results of evaluation of three \sa models. First column lists
linguistic capability for \sa task, and Columns 2-3 show the number of
seed and expanded test cases respectively. Columns 4-5 show the
failure rate in percentage by running the \sa models on the seed and
expanded test cases respectively. Column 6 shows the number of
expanded test cases failed, but their seed test cases passed. For LC9,
we combine two

From the
table, we can observe that

\subsection{RQ3: Test Suite Diversity}
\input{CM/coverage}

\subsection{RQ4: Use \tool for Debugging}

>>>>

This section presents experiment results and answer the RQs by
studying the results quantitatively and qualitatively.

\InputWithSpace{tables/test-results-table}

\subsection{RQ1: Test Suite Diversity}

Our experimental results show that \emph{\tool generated many test cases that the sentiment analysis models failed to predict the correct labels, and it produced significantly more diverse test cases than \Cklst did.}

Table~\ref{table:TestResult} shows the testing results of three \sa models. First column lists 
linguistic capabilities for the \sa task, and Columns 2-3 show 
the numbers of seed and expanded test cases, respectively. 
Columns 4-5 show the failure rate (i.e., percentage of test cases that a model predicts incorrect label) of each \sa models on the seed and expanded test cases respectively. 
Column 6 shows the number of expanded test cases that failed,
but their corresponding seed test cases passed.

We observe that in all but one linguistic capabilities,
\tool produces hundreds of test cases, expanding at least an order of magnitude more test cases than the seeds.
LC3 is an outlier; the 50 randomly selected
seeds in this linguistic capability did not produce any validated
expansions.
LC1 and LC5 have 19 and 26 seeds,
respectively. This means that \tool's search rules and transformation templates of these two linguistic capabilities produced few seeds.
Nevertheless, the syntax-base sentence expansion phase allows generation of 210 and 1009 test cases, respectively.

In terms of \sa model performance, all
three models achieve low failure rates in LC9 and LC2 while the failure rates are high in all other linguistic capabilities (26\%-100\%). We also observe that there are significant number of expanded test cases that failed, but their corresponding seeds did not (last column in Table \ref{table:TestResult}). This shows that the syntax-based sentence expansion phase indeed introduces more diverse sentence structures in the test cases that cause the models to fail.
% It finally
% shows usefulness of \tool since the different test results between
% seed and expanded cases provide accurate guidance for debugging model.

\input{CM/coverage}

\InputWithSpace{tables/manual-study-table}

\subsection{RQ2: Correctness of Sentiment Labels}
Table~\ref{table:ManualStudy} shows results of our manual study. The first column distinguishes the seed and expanded sentences. The number of test cases used for the study is represented in the
second column. The label consistency score defined
in Equation~\ref{metric:srel} is shown in column 3.

We observe that \emph{\tool generates test cases that consistently
  label their sentiment correctly.}  Column 3 shows that the label
consistency scores are 0.83 and 0.84 for the seed and expanded
sentences, respectively.
This means that \tool generates test oracles consistent with
human understanding most of the time. Also, there is
little difference of the scores between the seed and expanded
sentences. This implies that the syntax-based sentence expansion in
\tool preserves the sentiment as its seed.

% \sw{This paragraph is problematic. We are saying the inconsistency is just caused by human, indicating our tool is always correct?} Nevertheless, there exist inconsistency between \tool and manual labels. The causes of inconsistency are twofold. First, complicated sentences have led the participants to
% misunderstand its meaning. Second, phrase in a sentence has
% multiple interpretations of its sentiment. For example, the
% word ``easy'' could be interpreted as both compliment and back-handed
% insult.  
%% \sw{What are
%%   the causes of inconsistency? Looks like the main source of
%%   inconsistency comes from seed generation? Any insights on how it
%%   happened (e.g., issue with original labels, search rules, or
%%   templates?}

\subsection{RQ3: Correctness of Linguistic Capability Categorization}

The \lc relevancy score defined
in Equation~\ref{metric:lcrel} is shown in Column 4 of Table \ref{table:ManualStudy}. The result shows that
\emph{\tool generates test cases that are correctly categorized to the corresponding linguistic capabilities most of the time.}
The \lc relevancy scores for the seed and expanded sentences are both 0.9, achieving high order of agreement with human assessment. The fact that the expanded sentences
generated by \tool also have the same level of \lc
relevancy as the seed sentences shows that the syntax-based sentence expansion retains the linguistic capabilities.

\subsection{RQ4: Use \tool for Understanding Errors}

\begin{figure*}
    \centering
    \includegraphics[width=0.99\textwidth]{figs/explain.pdf}
    \vspace{-4mm}
    \caption{Visualization of the buggy reason of two \tool generated test cases.}
    \label{fig:explain}
\end{figure*}

Recall our RQ4 is to generate a template that will dominate the NLP model prediction to assist developers in understanding the false predictions. Figure \ref{fig:explain} shows the generated templates for two randomly selected seed inputs and corresponding generated test inputs.
The first example is to test ``sentiments in (question, yes) form'' (LC9), and the second example is to test ``negative positive with neutral content in the middle''  (LC7).
The first column contains the seed sentence, the second contains the generated sentence, and the third contains thCT  of each token's contribution score. The blue bar indicates thxe score for seed inputs, whereas the orange bar reflects the score f CTor created sentences.
We highlight the mutated token with yellow background and generated templates with red text.

The results show that after mutating the seed sentence with one token, the token set that dominates the NLP model prediction has changed.
We can trace the root causes to the bias of training data on the \lc under test; as a result, for the \lc under test, the model has a bias towards positive/negative for certain token sequence patterns. For example, \lc 9 has a bias toward the token sequence pattern that includes "maybe .... but ... even... yes". Thus, adding the token "even" to the seed sentence will match one of those biased sequence patterns.
Sentences with s.8gmxuin the training dataset are dominantly positive, thus the models makes the wrong decision on the sentence with ``even'' as positive. 
The visualization of each token's contribution score in the third column also confirms our observation. Once  ``even'' is added, scores of other tokens such as ``but'' and ``yes'' all change from negative to positive.
To fix the issue for LC9, we ne ed to add more training negative samples with the 还 of ``maybe . .. but ... even ... yes''.
%he experimental results in Fig. \ref{fig:explain} illustrate that \tool can help developers to understand the buggy reason of the misclassification go no在，
